### 2016-12-14 Writing/draft.tex
Updated methods

We simulated discrete morphological matrices based on the \texttt{dispRity R} package \citep[][; \url{https://github.com/TGuillerme/dispRity}]{thomas_guillerme_2016_55646}.

@@

@@

@@

\cite{Guillerme2016146}

@@

We applied the same procedure described above to 100 empirical matrices downloaded from TreeBASE (\url{http://treebase.org/}).
The 100 matrices where selected to be the most representative of empirical work with discrete morphological data: with randomly selected matrices with more than 100 each, published between 1985 and 2013 and covering 19 taxonomic classes within 6 phyla (Chordata, Arthropoda, Annelida, Angiosperm, Gymnosperm and Pteridophyta).
The full list of matrices is available in the supplementary materials @@@.

>>>>

To simulate the matrices we applied a protocol similar to \citep{Guillerme2016146}.
First, we generate random birth-death trees with the birth ($\lambda$) and death ($\mu$) parameters sampled from a uniform ($0$,$1$) distribution maintaining $\lambda$ $>$ $\mu$ using the diversitree \texttt{R} package \citep[v0.9-8;][]{fitzjohndiversitree2012} and saving the tree after reaching either 25, 75 or 150 taxa.
For each tree, we arbitrarily set the outgroup to be the first taxa (alphabetically) thus effectively rooting the trees on this taxa.
These trees are hereafter called the ``true'' trees.
We then simulated the characters using the either of the two following models:
\begin{itemize}
    \item The HKY-binary model \citep{OReilly20160081} which is an HKY model \citep{HKY85} with a random states frequency (sampled from a uniform distribution an scale to sum to one) and using a transition/transvertion rate of two \citep{douadycomparison2003} but where the purines (AG) were changed into state $0$ and the pyrimidines (CT) in state $1$.
    This model has the advantage of not favouring Bayesian inference \citep[since it doesn't use a M$k$ model;][]{OReilly20160081} but can only generate binary state characters.
    \item To generate more that two states characters, we used the M$k$ model \citep{lewisa2001}.
    We draw the number of character states with a probability of $0.85$ for two-state characters (binary) and $0.15$ for three state characters \citep{Guillerme2016146}.
    Assuming the same transition rate between character states might seem unrealistic and ignoring characters following, for example, a Dollo pattern, \cite{Wright01072016} have shown that an equal rate transition is still strictly majority in empirical data.
\end{itemize}

For each character, both models (HKY-binary or M$k$) where chosen randomly and ran with an overall evolutionary rate drawn from a gamma distribution ($\beta$ = $100$ and $\alpha$ = $3$).
We resimulated every invariant characters to obtain a matrix with no invariant characters.
Choosing these low evolutionary rate values allowed us to obtain discrete characters matrices with realistic values of Consistency Indices that where superior that $0.26$ \citep{OReilly20160081}.
For each trees with 25, 75 or 150 taxa we generated matrices with 100, 350 and 1000 characters following \cite{OReilly20160081}.
The matrices where generated using the \texttt{dispRity R} package \citep[][; \url{https://github.com/TGuillerme/dispRity}]{thomas_guillerme_2016_55646}.
To estimate the variance of our simulations and assess the effect of our random parameters, we repeated this step 50 times resulting in 450 morphological matrices (hereafter called the ``normal'' matrices).

@@

We then calculated the pairwise character differences for each generated matrices. 
We then modified the matrices to either maximise or minimise the pairwise character differences for each matrices using three different algorithms.
For maximising the pairwise differences between characters, we selected the characters that where the most similar to all the others (i.e. with an average character difference $<$$0.25$) and replaced them randomly by any of the remaining characters.
This operation increased the overall pairwise character difference in the matrix thus making the characters more dissimilar.
Conversely, for minimising the pairwise character differences, we selected the most dissimilar characters (i.e. with an average character difference $<$$0.75$) and randomly replaced them with the remaining ones.
Finally, because this operation effectively changes the weight of characters (i.e. giving the characters $<$$0.25$ or $>$$0.75$ a weight of $0$ and giving the randomly selected characters to replace them a weight of +$1$), we randomly replaced the average number of characters replaced in the character maximisation and minimisation by any other characters as a null expectation modification (i.e. randomly weighting characters).
This step resulted in a total of 1800 matrices (hereafter called the ``maximised'', ``minimised'' and ``random'' matrices).
The algorithms for the three modifications is available on GitHub@@@. %TG: "@@@" is my "to replace" sign.

@@

We inferred the topologies in both Bayesian and Parsimony using MrBayes and PAUP* respectively.
Bayesian settings.
PAUP ``settings''.

@@

We compared the topologies using the same approach as in \cite{Guillerme2016146}.

@@

We applied the same procedure described above (without the morphological matrices simulation) to 100 empirical matrices downloaded from TreeBASE (\url{http://treebase.org/}).
The 100 matrices where selected to be the most representative of empirical work with discrete morphological data: with randomly selected matrices with more than 100 each, published between 1985 and 2013 and covering 19 taxonomic classes within 6 phyla (Chordata, Arthropoda, Annelida, Angiosperm, Gymnosperm and Pteridophyta).
The full list of matrices is available in the supplementary materials @@@.
